Applications of Even-point Muiltiloop Unitarity: Exponentiation, Anomalies and Evanescence

### 2023-05-30 eventPointTwoLoop.tex
fiddling

\newcommand{\cC}{g} % -- Crossing Count symbol.
\newcommand{\cHL}[0]{C^{\text{H.L.}}}

@@

\paragraph{\textbf{Construction via EMU}} Using the four-point NLSM amplitude defined above, the off-shell bubble integral has a numerator simply given by the bubble's two-particle cut.

@@

\scaleIntApion = \sum_{\text{states}}\int \frac{d^D l}{(2\pi)^D} \frac{\mathcal{A}^{\text{NLSM}}_{(\bar{l}_1|12|\bar{l}_2)}\mathcal{A}^{\text{NLSM}}_{(l_2|34|l_1)}}{l^2(l+k_{12})^2}\,.

>>>>

\newcommand{\cC}{g} % -- Crossing Count symbol.
\newcommand{\cHL}[0]{C^{\text{H.L.}}}
\newcommand{\nbub}[0]{N^{\text{bub}}}

@@

\paragraph{\textbf{Construction}} Using the four-point NLSM amplitude defined above,  the off-shell bubble integral has a numerator simply given by the bubble's two-particle cut.
\begin{align}
\nbub &=  \sum_{\text{states}} \frac{\mathcal{A}^{\text{NLSM}}_{(\bar{l}_1|12|\bar{l}_2)}\mathcal{A}^{\text{NLSM}}_{(l_2|34|l_1)}}\\
 &= \frac{\mathcal{A}^{\text{NLSM}}_{(\bar{l}_1|12|\bar{l}_2)}\mathcal{A}^{\text{NLSM}}_{(l_2|34|l_1)}} \\
 &=
\end{align}

@@

\scaleIntApion =\int \frac{d^D l}{(2\pi)^D} \frac{ \sum_{\text{states}} \mathcal{A}^{\text{NLSM}}_{(\bar{l}_1|12|\bar{l}_2)}\mathcal{A}^{\text{NLSM}}_{(l_2|34|l_1)}}{l^2(l+k_{12})^2}\,.
